Robust and Efficient CSI Compression Using CLLWCsiNet in Noisy MIMO Environments

### 2025-04-06 paper_latex_edit - Copy.tex
✅ Citation-rich Multi-Head Transformer Architecture with Higher Dimensional Feature Representation for Massive MIMO CSI Feedback

@@

>>>>

\cite{chen2024transnet} propose TransNet+, an enhanced Transformer-based architecture for massive MIMO CSI feedback. The method improves upon existing Transformer designs by incorporating higher-dimensional feature representations and an optimized multi-head attention mechanism. A warm-up-aided cosine training scheme is introduced to accelerate convergence and enhance feature learning. Experimental results demonstrate superior performance compared to state-of-the-art methods, particularly at high compression ratios, with significant NMSE reduction in both indoor and outdoor scenarios.

@@

	\bibitem{chen2024transnet}
	Q. Chen, A. Guo, and Y. Cui, ``Multi-head transformer architecture for massive MIMO CSI feedback,'' \textit{Appl. Sci.}, vol. 14, no. 3, p. 1356, 2024.
